### 2018-10-16 tex/evaluation.tex
fzw revision

Figure \ref{fig:hadoop_terasort} shows the hardware resource utilization of Hadoop MapReduce running Terasort. Both figures have the same proportion of time. Hadoop MapReduce with SCache brings 15\% of total time optimization with 384GB input data size. 
As shown in the Figure \ref{fig:hadoop_terasort_origin}, Hadoop MapReduce without SCache writes intermediate data locally in the Map phase. The shuffle phase and reduce phase start simultaneously. Because the large amount of shuffle data reaches the network bottleneck, the beginning part of reduce needs to wait needs to wait for network transfer. This causes the CPU resources to be idle. 
As shown in the Figure \ref{fig:hadoop_terasort_scache}, Hadoop Madpreduce with SCache start pre-fetching in the Map phase. This avoids the Reduce phase waiting for the shuffle data. Furthermore, pre-fetching utilizes the idle IO throughput in the Map phase. As shown in Figure \ref{fig:hadoop_terasort_time}, after better fine-grained utilization of hardware resources, Hadoop MapReduce with SCache optimize Terasort overall completion time by up to 15\% and an average of 13\% with input data sizes from 128GB to 512GB.
}

>>>>

Figure \ref{fig:hadoop_terasort} shows the hardware resource utilization of Hadoop MapReduce running Terasort. Both figures have the same proportion of time. Hadoop MapReduce with SCache brings 15\% of total time optimization with 384GB input data size. 
As shown in the Figure \ref{fig:hadoop_terasort_origin}, Hadoop MapReduce without SCache writes intermediate data locally in the map phase. The shuffle phase and reduce phase start simultaneously. Because the large amount of shuffle data reaches the network bottleneck, the beginning part of reduce needs to wait needs to wait for network transfer. This causes the CPU resources to be idle. 
As shown in the Figure \ref{fig:hadoop_terasort_scache}, Hadoop Madpreduce with SCache start pre-fetching in the map phase. This avoids the reduce phase waiting for the shuffle data. Furthermore, pre-fetching utilizes the idle IO throughput in the map phase. As shown in Figure \ref{fig:hadoop_terasort_time}, after better fine-grained utilization of hardware resources, Hadoop MapReduce with SCache optimize Terasort overall completion time by up to 15\% and an average of 13\% with input data sizes from 128GB to 512GB.
}

### 2018-10-16 tex/impl.tex
fzw revision

\section{Implementation}\label{impl}
This section presents an overview of the implementation of SCache. 
% {\color{red}
% Here we use Spark as an example of DAG framework to illustrate the work flow of shuffle optimization. 
% We will first present the system overview in Subsection \ref{arch} while the following two subsections focus on the two constraints on memory management.
% }
{\color{blue}
We first present the system overview in Subsection \ref{arch} and the detail of sampling in Subsection\ref{sampling}. 
The following two subsections focus on the two constraints on memory management.
In Subsection \ref{crossframework}, we will evaluate cross-framework capability of SCache based on Hadoop MapReduce and Spark. 
At last, we discuss the cost of adapting SCache and the fault tolerance. 
}

\subsection{System Overview}\label{arch}
SCache consists of three components: a distributed shuffle data management system, a DAG co-scheduler, and a %{\color{red}daemon inside Spark.}
{\color{blue} worker daemon. As a plug-in system, SCache needs to rely on a DAG framework.} As shown in Figure \ref{fig:architecture}, SCache employs the legacy master-slaves architecture like GFS \cite{gfs} for shuffle data management system. 
The master node of SCache coordinates the shuffle blocks globally with application context. The worker node reserves memory to store blocks.
The coordination provides two guarantees: (a)data is stored in memory before tasks start and (b)data is scheduled on-off memory with all-or-nothing and context-aware constraints. 
The daemon bridges the communication between %{\color{red}Spark}
{\color{blue} DAG framework} and SCache. The co-scheduler is dedicated to pre-schedule reduce tasks with DAG information and enforce the scheduling results to %{\color{red}Spark scheduler}
 {\color{blue} original scheduler in framework master}.

SCache consists of three components: a distributed shuffle data management system, a DAG co-scheduler, and a {\color{blue} worker daemon}. As shown in Figure \ref{fig:arch}, SCache employs the legacy master-slaves architecture like GFS \cite{gfs} for shuffle data management system.

The master node of SCache coordinates the shuffle blocks globally with application context. The worker node reserves memory to store blocks.
The coordination provides two guarantees: (a)data is stored in memory before tasks start and (b)data is scheduled on-off memory with all-or-nothing and context-aware constraints. 
The daemon bridges the communication between {\color{blue}DAG framework} and SCache. The co-scheduler is dedicated to pre-schedule reduce tasks with DAG information and enforce the scheduling results to {\color{blue} original scheduler in framework master}.

% {\color{red}
% When a Spark job starts, the DAG will be first generated. 
% During the DAG generation, the shuffle dependencies among Resilient Distributed Datasets (RDDs) will then be submitted through the daemon process in Spark driver. 
% }
{\color{blue}
When a DAG job is submitted, the DAG information will be generated in framework master scheduler. 
Before the computing tasks begin, the shuffle dependencies are determined based on job configuration.
}
For each shuffle dependency, the shuffle ID, the type of partitioner, the number of map tasks, and the number of reduce tasks are included.  If there is a specialized partitioner, such as range partitioner, in the shuffle dependencies, the daemon will insert a sampling application before the {\color{blue}computing job}. We will elaborate the sampling procedure in the Section \ref{sampling}.
% \begin{minipage}{\columnwidth}
% \begin{algorithm}[H]
% \caption{Heuristic MinHeap Scheduling for Single Shuffle}
% \label{hminheap}
% 	\begin{algorithmic}[1]
% 	\small
% 	\Procedure{\Large schedule}{$m, host\_ids, p\_reduces$}
% 		\State $m\gets$ partition number of map tasks
% 		\State $R\gets$ sort $p\_reduces$ by size in descending order
% 		\State $M\gets$ min-heap $\left\{ host\_id \rightarrow \left( \left[ reduces \right], size \right) \right\}$
% 		\State $idx\gets$ len$\left(R\right) - 1$
% 		\While{$idx \geq 0$}
% 		\Comment{Schedule reduces by MinHeap}
% 		\State $M\left[0\right].size \mathrel{+}= R\left[idx\right].size$
% 		\State $M\left[0\right].reduces.append\left(R\left[idx\right]\right)$
% 		\State $R\left[idx\right].assigned\_host \gets M \left[0\right].host\_id$
% 		\State Sift down $M\left[0\right]$ by $size$
% 		\State $idx\gets idx-1$
% 		\EndWhile
% 		\State $max\gets$ maximum size in $M$
% 		\State Convert $M$ to mapping $\left\{ host\_id \rightarrow \left( \left[ rid\_arr \right], size \right) \right\}$
% 		\ForAll{$reduce$ in $R$}
% 		\Comment{Heuristic swap by locality}
% 			\If{$reduce.assigned\_id \neq reduce.host\_id$}
% 				\State $p\gets reduce.prob$
% 				\State $norm\gets \left(p-1/m\right)/\left(1-1/m\right)/10$
% 				\State $upper\_bound \gets \left(1 + norm\right) \times max$
% 				\State SWAP\_TASKS$\left(M, reduce, upper\_bound\right)$
% 			\EndIf
% 		\EndFor
% 		% \Comment{$m$ is the number of input data}
% 		% \Comment{$r$ is partition number of reduces}
% 		% \Comment{$hosts$ is array of (hostid, partitionids[], size)}
% 		% \Comment{$c$ is $r*m$ array of composition data}
% 		% \Comment{$pSize$ is $r$ size array of predicted size of reduces}
% 		\Return $M$
% 	\EndProcedure
% 	\Procedure{\Large swap\_tasks}{$M, reduce, upper\_bound$}
% 		\State $reduces \gets M\left[reduce.host\_id\right].reduce$	
% 		\State $candidates \gets$ Select from $reduces$ that $assigned\_id \neq host\_id$ \textbf{and} total size closest to $reduce.size$
% 		\State $\Delta size \gets sizeOf\left(candidates\right) - reduce.size$
% 		\State $size\_host \gets M\left[reduce.host\_id\right].size - \Delta size$
% 		\State $size\_assigned \gets M\left[reduce.assigned\_id\right].size + \Delta size$
% 		\If{$size\_host\leq upper\_bound$ \textbf{and} \\
% 			\qquad \; $size\_assigned\leq upper\_bound$}
% 			\State Swap $candidates$ and $reduce$
% 			\State Update $size$ in $M$
% 			\State Update $assigned\_host$ in $candidates$ and $reduce$
% 		\EndIf
% 	\EndProcedure
% 	\end{algorithmic}
% \end{algorithm}
% \end{minipage}

When a map task finishes computing, the shuffle write implementation of DAG framework is modified to call the SCache API and move all the blocks out of {\color{blue}framework worker} through memory copy. 
After that the slot will be released (without blocking on disk operations).
When a block of the map output (i.e., "map output" in Figure \ref{fig:shuffle}) is received, the SCache worker will send the block ID and the size to the master.
If the collected map output data reach the observation threshold, the DAG co-scheduler will run the scheduling Algorithm \ref{hminheap} or \ref{mhminheap} to pre-schedule the reduce tasks and then broadcast the scheduling result to start pre-fetching on each worker.
% After that, when a map task is finished, each node will receive a broadcast message. 
SCache worker will filter the reduce tasks' IDs that are scheduled on itself and start pre-fetching shuffle data from the remote. 
% {\color{red}
% To enforce SCache pre-scheduled tasks -- node mapping, we insert some lines of codes in Spark DAG Scheduler.
% For RDDs with shuffle dependencies, Spark DAG scheduler will consult SCache master to get the preferred location for each partition and set \textit{NODE\_LOCAL} locality level on corresponding reduce tasks.
% }
{\color{blue}
In order to force DAG framework to run according to the SCache pre-scheduled results, we insert some lines of codes in framework scheduler.
After modification, DAG scheduler will consult SCache co-scheduler to get the preferred location for each task.
}
% In the case of extreme skew scenario, such as Figure \ref{fig:range_pre_sample}, Heuristic MinHeap trades about 0.05\% percent of stage completion time for 99\% reduction of shuffle data transmission through network by heuristicly swapping tasks.
% \begin{minipage}{\columnwidth}
% \begin{algorithm}[H]
% \caption{Accumulate Heuristic Scheduling for Multi-Shuffles}
% \label{mhminheap}
% 	\begin{algorithmic}[1]
% 	\small
% 	\Procedure{\Large m\_schedule}{$m, host\_id, p\_reduces, shuffles$}
% 		\State $m\gets$ partition number of map tasks
% 		\Comment $shuffles$ is the previous schedule result 
% 		\ForAll{$r$ in $p\_reduces$}
% 			\State $r.size \mathrel{+}= shuffles\left[r.rid\right].size$
% 			\If{$shuffles\left[r.rid\right].size\geq r.size \times r.prob$}
% 				\State $r.prob\gets shuffles\left[r.rid\right].size / r.size$
% 				\State $r.host\_id\gets shuffles\left[r.rid\right].assigned\_host$
% 			\EndIf
% 		\EndFor
% 		\State $M\gets$ $SCHEDULE\left(m, host\_id, p\_reduces\right)$
% 		\ForAll{$host\_id$ in $M$}
% 			\Comment Re-shuffle
% 			\ForAll{$r$ in $M\left[host\_id\right].reduces$}
% 				\If{$host\neq shuffles\left[r.rid\right].assigned\_host$}
% 				\State Re-shuffle data to $host$
% 				\State $shuffles\left[r.rid\right].assigned\_host\gets host$
% 				\EndIf
% 			\EndFor
% 		\EndFor
% 		\Return $M$
% 	\EndProcedure
% 	\end{algorithmic}
% \end{algorithm}
% \end{minipage}

@@

% {\color{red}
% \subsection{Cost of adapting DAG frameworks}
% SCache provides API through RPC, such as \textit{putBlock(blockId)}, \textit{getBlock(blockId)}, and \textit{getScheduleResult(shuffleId)}. The concise design makes it easy to adapt DAG frameworks to enable SCache optimization. For example, it only takes about 500 lines of code in Spark to integrate SCache. By a glance of Hadoop source code, we believe that the costs of enabling SCache on MapReduce \cite{hadoop} and YARN \cite{yarn} based DAG computing framework, such as Tez \cite{tez}, are also very low.
% }
{\color{blue}
\subsection{Analysis of cross-framework capability}\label{crossframework}
Shuffle optimization of SCache inevitably requires modification on dependent DAG framework. SCache provides API through RPC, such as \textit{putBlock (blockId)}, \textit{getBlock (blockId)}, and \textit{getScheduleResult (shuffleId)}. In order to use SCache, we mainly need to modify the two parts of the framework: (a)We need to insert codes in the DAG scheduler to let framework provide DAG information and follow the order. (b)The shuffle data between the Map task and the Reduce task should be transfer to SCahce Storge Management.

To prove the cross-framework capability of SCache, we implement SCache on Hadoop MapReduce and Spark respectively. Taking Hadoop MapReduce as an example, we insert codes in ResourceManager and modify codes in MapTask and ReduceTask to call SCache API through RPC. It takes about 400 lines of code. In Spark, we mainly modified the DAGScheduler and the corresponding data fetcher. 
It only takes about 500 lines of code. Such hundreds of lines of code modification are very small compared to the hundreds of thousands of lines of code in DAG framework. we believe that the costs of enabling SCache on other DAG computing frameworks, such as Tez \cite{tez}, are also very low.
}

>>>>

\section{Implementation}\label{impl}
This section presents an overview of the implementation of SCache. 
% {\color{red}
% Here we use Spark as an example of DAG framework to illustrate the work flow of shuffle optimization. 
% We will first present the system overview in Subsection \ref{arch} while the following two subsections focus on the two constraints on memory management.
% }
{\color{blue}
We first present the system overview and the detail of sampling in Subsection \ref{arch}. 
The following \ref{memorymanage} subsection focuses on the two constraints on memory management.
In Subsection \ref{crossframework}, we will evaluate cross-framework capability of SCache based on Hadoop MapReduce and Spark. 
At last, we discuss the cost of adapting SCache and the fault tolerance. 
}

\subsection{System Overview}\label{arch}
SCache consists of three components: a distributed shuffle data management system, a DAG co-scheduler, and a %{\color{red}daemon inside Spark.}
{\color{blue} worker daemon. As a plug-in system, SCache needs to rely on a DAG framework.} As shown in Figure \ref{fig:architecture}, SCache employs the legacy master-slaves architecture like GFS \cite{gfs} for shuffle data management system. 
The master node of SCache coordinates the shuffle blocks globally with application context. The worker node reserves memory to store blocks.
The coordination provides two guarantees: (a)data is stored in memory before tasks start and (b)data is scheduled on-off memory with all-or-nothing and context-aware constraints. 
The daemon bridges the communication between %{\color{red}Spark}
{\color{blue} DAG framework} and SCache. The co-scheduler is dedicated to pre-schedule reduce tasks with DAG information and enforce the scheduling results to %{\color{red}Spark scheduler}
 {\color{blue} original scheduler in framework}.

% SCache consists of three components: a distributed shuffle data management system, a DAG co-scheduler, and a {\color{blue} worker daemon}. As shown in Figure \ref{fig:arch}, SCache employs the legacy master-slaves architecture like GFS \cite{gfs} for shuffle data management system.

% The master node of SCache coordinates the shuffle blocks globally with application context. The worker node reserves memory to store blocks.
% The coordination provides two guarantees: (a)data is stored in memory before tasks start and (b)data is scheduled on-off memory with all-or-nothing and context-aware constraints. 
% The daemon bridges the communication between {\color{blue}DAG framework} and SCache. The co-scheduler is dedicated to pre-schedule reduce tasks with DAG information and enforce the scheduling results to {\color{blue} original scheduler in framework master}.

% {\color{red}
% When a Spark job starts, the DAG will be first generated. 
% During the DAG generation, the shuffle dependencies among Resilient Distributed Datasets (RDDs) will then be submitted through the daemon process in Spark driver. 
% }
{\color{blue}
When a DAG job is submitted, the DAG information will be generated in framework task scheduler. 
Before the computing tasks begin, the shuffle dependencies are determined based on DAG.
}
For each shuffle dependency, the shuffle ID, the type of partitioner, the number of map tasks, and the number of reduce tasks are included.  If there is a specialized partitioner, such as range partitioner, in the shuffle dependencies, the daemon will insert a sampling application before the {\color{blue}computing job}. We will elaborate the sampling procedure in the Section \ref{sampling}.
% \begin{minipage}{\columnwidth}
% \begin{algorithm}[H]
% \caption{Heuristic MinHeap Scheduling for Single Shuffle}
% \label{hminheap}
% 	\begin{algorithmic}[1]
% 	\small
% 	\Procedure{\Large schedule}{$m, host\_ids, p\_reduces$}
% 		\State $m\gets$ partition number of map tasks
% 		\State $R\gets$ sort $p\_reduces$ by size in descending order
% 		\State $M\gets$ min-heap $\left\{ host\_id \rightarrow \left( \left[ reduces \right], size \right) \right\}$
% 		\State $idx\gets$ len$\left(R\right) - 1$
% 		\While{$idx \geq 0$}
% 		\Comment{Schedule reduces by MinHeap}
% 		\State $M\left[0\right].size \mathrel{+}= R\left[idx\right].size$
% 		\State $M\left[0\right].reduces.append\left(R\left[idx\right]\right)$
% 		\State $R\left[idx\right].assigned\_host \gets M \left[0\right].host\_id$
% 		\State Sift down $M\left[0\right]$ by $size$
% 		\State $idx\gets idx-1$
% 		\EndWhile
% 		\State $max\gets$ maximum size in $M$
% 		\State Convert $M$ to mapping $\left\{ host\_id \rightarrow \left( \left[ rid\_arr \right], size \right) \right\}$
% 		\ForAll{$reduce$ in $R$}
% 		\Comment{Heuristic swap by locality}
% 			\If{$reduce.assigned\_id \neq reduce.host\_id$}
% 				\State $p\gets reduce.prob$
% 				\State $norm\gets \left(p-1/m\right)/\left(1-1/m\right)/10$
% 				\State $upper\_bound \gets \left(1 + norm\right) \times max$
% 				\State SWAP\_TASKS$\left(M, reduce, upper\_bound\right)$
% 			\EndIf
% 		\EndFor
% 		% \Comment{$m$ is the number of input data}
% 		% \Comment{$r$ is partition number of reduces}
% 		% \Comment{$hosts$ is array of (hostid, partitionids[], size)}
% 		% \Comment{$c$ is $r*m$ array of composition data}
% 		% \Comment{$pSize$ is $r$ size array of predicted size of reduces}
% 		\Return $M$
% 	\EndProcedure
% 	\Procedure{\Large swap\_tasks}{$M, reduce, upper\_bound$}
% 		\State $reduces \gets M\left[reduce.host\_id\right].reduce$	
% 		\State $candidates \gets$ Select from $reduces$ that $assigned\_id \neq host\_id$ \textbf{and} total size closest to $reduce.size$
% 		\State $\Delta size \gets sizeOf\left(candidates\right) - reduce.size$
% 		\State $size\_host \gets M\left[reduce.host\_id\right].size - \Delta size$
% 		\State $size\_assigned \gets M\left[reduce.assigned\_id\right].size + \Delta size$
% 		\If{$size\_host\leq upper\_bound$ \textbf{and} \\
% 			\qquad \; $size\_assigned\leq upper\_bound$}
% 			\State Swap $candidates$ and $reduce$
% 			\State Update $size$ in $M$
% 			\State Update $assigned\_host$ in $candidates$ and $reduce$
% 		\EndIf
% 	\EndProcedure
% 	\end{algorithmic}
% \end{algorithm}
% \end{minipage}

When a map task finishes computing, the shuffle write implementation of DAG framework is modified to call the SCache API and move all the blocks out of {\color{blue}framework worker} through memory copy. 
After that the slot will be released (without being blocked on disk operations).
When a block of the map output (i.e., "map output" in Figure \ref{fig:shuffle}) is received, the SCache worker will send the block ID and the size to the master.
If the collected map output data reach the observation threshold, the DAG co-scheduler will run the scheduling Algorithm \ref{hminheap} or \ref{mhminheap} to pre-schedule the reduce tasks and then broadcast the scheduling result to start pre-fetching on each worker.
% After that, when a map task is finished, each node will receive a broadcast message. 
SCache worker will filter the reduce tasks' IDs that are scheduled on itself and start pre-fetching shuffle data from the remote. 
% {\color{red}
% To enforce SCache pre-scheduled tasks -- node mapping, we insert some lines of codes in Spark DAG Scheduler.
% For RDDs with shuffle dependencies, Spark DAG scheduler will consult SCache master to get the preferred location for each partition and set \textit{NODE\_LOCAL} locality level on corresponding reduce tasks.
% }
{\color{blue}
In order to force DAG framework to run according to the SCache pre-scheduled results, we insert some lines of codes in framework scheduler.
After modification, DAG scheduler will consult SCache co-scheduler to get the preferred location for each task.
}
% In the case of extreme skew scenario, such as Figure \ref{fig:range_pre_sample}, Heuristic MinHeap trades about 0.05\% percent of stage completion time for 99\% reduction of shuffle data transmission through network by heuristicly swapping tasks.
% \begin{minipage}{\columnwidth}
% \begin{algorithm}[H]
% \caption{Accumulate Heuristic Scheduling for Multi-Shuffles}
% \label{mhminheap}
% 	\begin{algorithmic}[1]
% 	\small
% 	\Procedure{\Large m\_schedule}{$m, host\_id, p\_reduces, shuffles$}
% 		\State $m\gets$ partition number of map tasks
% 		\Comment $shuffles$ is the previous schedule result 
% 		\ForAll{$r$ in $p\_reduces$}
% 			\State $r.size \mathrel{+}= shuffles\left[r.rid\right].size$
% 			\If{$shuffles\left[r.rid\right].size\geq r.size \times r.prob$}
% 				\State $r.prob\gets shuffles\left[r.rid\right].size / r.size$
% 				\State $r.host\_id\gets shuffles\left[r.rid\right].assigned\_host$
% 			\EndIf
% 		\EndFor
% 		\State $M\gets$ $SCHEDULE\left(m, host\_id, p\_reduces\right)$
% 		\ForAll{$host\_id$ in $M$}
% 			\Comment Re-shuffle
% 			\ForAll{$r$ in $M\left[host\_id\right].reduces$}
% 				\If{$host\neq shuffles\left[r.rid\right].assigned\_host$}
% 				\State Re-shuffle data to $host$
% 				\State $shuffles\left[r.rid\right].assigned\_host\gets host$
% 				\EndIf
% 			\EndFor
% 		\EndFor
% 		\Return $M$
% 	\EndProcedure
% 	\end{algorithmic}
% \end{algorithm}
% \end{minipage}

@@

% {\color{red}
% \subsection{Cost of adapting DAG frameworks}
% SCache provides API through RPC, such as \textit{putBlock(blockId)}, \textit{getBlock(blockId)}, and \textit{getScheduleResult(shuffleId)}. The concise design makes it easy to adapt DAG frameworks to enable SCache optimization. For example, it only takes about 500 lines of code in Spark to integrate SCache. By a glance of Hadoop source code, we believe that the costs of enabling SCache on MapReduce \cite{hadoop} and YARN \cite{yarn} based DAG computing framework, such as Tez \cite{tez}, are also very low.
% }
{\color{blue}
\subsection{Analysis of cross-framework capability}\label{crossframework}
Shuffle optimization of SCache inevitably requires modification on dependent DAG framework. SCache provides API through RPC, such as \textit{putBlock (blockId)}, \textit{getBlock (blockId)}, and \textit{getScheduleResult (shuffleId)}. In order to use SCache, we mainly need to modify the two parts of the framework: (a)We need to insert codes in the DAG scheduler to let framework provide DAG information and follow pre-scheduled result of SCache. (b)The shuffle data between the Map task and the Reduce task should be transfered to SCahce Storge Management.

To prove the cross-framework capability of SCache, we adapt SCache on Hadoop MapReduce and Spark respectively. Taking Hadoop MapReduce as an example, we insert codes in ResourceManager and modify codes in MapTask and ReduceTask to call SCache API through RPC. It takes about 400 lines of code. In Spark, we mainly modified the DAGScheduler and the corresponding data fetcher. 
It only takes about 500 lines of code. Such hundreds of lines of code modification are very small compared to the hundreds of thousands of lines of code in DAG framework. we believe that the costs of enabling SCache on other DAG computing frameworks, such as Tez \cite{tez}, are also very low.
}

### 2018-10-16 tex/intro.tex
fzw revision

{\color{blue}
In order to visually analyze above-mentioned resources scheduling, we propose a performance model called \textit{Framework Resources Quantification} (FRQ) model. FRQ model quantifies computing and I/O resources and displays resources scheduling strategy of DAG framework in time dimension. We use FRQ model to assist in analyze the deficiencies of resources scheduling and optimize it. 
FRQ model has five parameters: \textit{Input Data Size, Data Conversion Rate, Computation Round Number, Computation Speed,} and \textit{Shuffle  Speed}.
According to the above five parameters and the scheduling strategy of the DAG framework, FRQ model is able to calculate the execution time of each phase of a computing job. 
Take Apache Hadoop MapReduce as a simple DAG computing example, we use FRQ to model each phases of the computing, including Map, Shuffle, and Reduce.
By revealing the relationships between the various phases, FRQ model assist us in discovering the irrationality of resource scheduling during computing.
I/O resource in Map phase is not fully utilized. Furthermore, due to coupling with reduce phase, shuffle phase delays the execution time of reduce phase. 
This situation will be amplified in shuffle-sensitive tasks.
}

@@

{\color{blue}
We have implemented SCache, a customized Apache Spark \cite{apachespark} and a customized Apache Hadoop. We have also designed a performance model called \textit{Framework Resources Quantification} (FRQ) model to analyze the shuffle optimization of SCache and calculate the execution time of each phase of computing job. The performance of SCache is evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster on both Apache Spark and Apache Hadoop. On Apache Spark, we conduct basic test GroupByTest. We also evaluate Terasort\footnote{https://github.com/ehiggs/spark-terasort} benchmark and standard workloads like TPC-DS\footnote{http://www.tpc.org/tpcds/} for multi-tenant modeling. On Apache Hadoop, we focus on Terasort benchmark. In a nutshell, SCache can eliminate explicit shuffle process by at most $89\%$ in varied application scenarios. More impressively, SCache reduces $~40\%$ of overall completion time of TPC-DS queries on average on Apache Spark. On Apache Hadoop, SCache optimize end-to-end Terasort completion time by 15\%.
}

>>>>

{\color{blue}
In order to visually analyze above-mentioned resources scheduling, we propose a performance model called \textit{Framework Resources Quantification} (FRQ) model. FRQ model quantifies computing and I/O resources and displays resources scheduling strategy of DAG framework in time dimension. We use FRQ model to assist in analyze the deficiencies of resources scheduling and optimize it. 
FRQ model has five parameters: \textit{Input Data Size, Data Conversion Rate, Computation Round Number, Computation Speed,} and \textit{Shuffle  Speed}.
According to the above five parameters and the scheduling strategy of the DAG framework, FRQ model is able to calculate the execution time of each phase of a computing job. 
Take Apache Hadoop MapReduce as a simple DAG computing example, we use FRQ to model each phases of the computing, including Map, Shuffle, and Reduce.
By revealing the relationships between the various phases, FRQ model assist us in discovering the irrationality of resource scheduling during computing.
I/O resource in map phase is not fully utilized. Furthermore, due to coupling with reduce phase, shuffle phase delays the execution time of reduce phase. 
This situation will be amplified in shuffle-heavy tasks.
}

@@

{\color{blue}
We have implemented SCache, a customized Apache Spark \cite{apachespark} and a customized Apache Hadoop. We have also designed a performance model called \textit{Framework Resources Quantification} (FRQ) model to analyze the shuffle optimization of SCache and calculate the execution time of each phase of computing job. The performance of SCache is evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster on both Apache Spark and Apache Hadoop. On Apache Spark, we conduct basic test \textit{GroupByTest}. We also evaluate Terasort\footnote{https://github.com/ehiggs/spark-terasort} benchmark and standard workloads like TPC-DS\footnote{http://www.tpc.org/tpcds/} for multi-tenant modeling. On Apache Hadoop, we focus on Terasort benchmark. In a nutshell, SCache can eliminate explicit shuffle process by at most $89\%$ in varied applications. More impressively, SCache reduces $~40\%$ of overall completion time of TPC-DS queries on average on Apache Spark. On Apache Hadoop, SCache optimize end-to-end Terasort completion time by 15\%.
}
